The bhsdtr package: a general purpose method of Bayesian inference for Signal Detection Theory models

### 2019-03-12 inst/preprint/paper.tex
submitted version
Corrected author note in the manuscript

\keywords{Signal Detection Theory, Bayesian inference, hierarchical
  models}

@@

\authornote{This research was supported in part by the National
  Science Centre, Poland HARMONIA grant given to Michal Wierzchon
  (2014/14/M/HS6/00911).

>>>>

\keywords{Signal Detection Theory, rating experiments, Bayesian
  inference, hierarchical models}

@@

\authornote{

  % This research was supported in part by the National
  % Science Centre, Poland HARMONIA grant given to Michal Wierzchon
  % (2014/14/M/HS6/00911).
